---
title: "<center>Reverse Engineering of the Neighborhood Atlas 2022 ADI Components</center>"
author: "<br><center>[Nicole Gladish, PhD](https://profiles.stanford.edu/nicole-gladish)</center>"
date: "<center>`r format(Sys.time(), '%d %B, %Y')`</center>"
output:
  html_document:
    includes:
      after_body: "../../templates/NG_footer.html"
      in_header: "../../templates/header.html"
    toc: true
    toc_depth: 2
    number_sections: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
    css: "../../templates/bootstrap.css"
    self_contained: true
---

<br><br>

```{css, echo = FALSE}
  /* General code block styling */
  pre {
    background-color: #2e2e2e;
    color: #f5f5f5;
    padding: 8px 12px;
    border-radius: 4px;
    font-family: "Courier New", monospace;
  }
  code {
      background-color: #2e2e2e;
    color: #f5f5f5;
    padding: 8px 12px;
    border-radius: 4px;
    font-family: "Courier New", monospace;
}
  .hljs{
  display: block;
  padding: 0.5em;
  background: #2e2e2e;
  color: #f5f5f5;
  }

  /* Strings */
  .hljs-string {
      color: #c2a3fd; 
  }

  /* Numbers */
  .hljs-number, 
  .hljs-literal,
  .hljs-logical,
  .hljs-built_in, 
  .hljs-variable.constant,
  .hljs-keyword, 
  .hljs-variable.language, 
  .hljs-title.function{
      color: #8fff84; 
  }

  /* Comments */
  .hljs-comment, .hljs-quote {
      color: #ff7777; 
  }

  /* Symbols and punctuation (e.g., parentheses, brackets) */
.hljs-punctuation, .hljs-operator {
      color: #13cee0; 
  }
  
  /* General card block styling */
  
div.card {
    background-color: #71797E; /* Dark background color */
    border-radius: 10px;
    padding: 10px;
    color: white; /* Set text color to white */
    margin-bottom: 0;
    margin-top: 10px; /* Add some space above paragraphs if needed */
  }
   /* Explicitly set all header text inside .card to white (in case bootstrap overrides it) */
  div.card h1, div.card h2, div.card h3, div.card h4, div.card h5, div.card h6 {
    color: white; /* Set header text color to white */
  }
```

```{r setup, include=FALSE}
## Warn if R version is older than what was used for this analysis
if (getRversion() < "4.5.0") {
  warning(
    "This analysis was developed under R 4.5.0 ",
    "You are using R ", as.character(getRversion()),
    ". If you see package errors, consider upgrading to at least R 4.5.0"
  )
}

## Check for required packages and fail with a clear message if missing
needed_pkgs <- c(
  "tidyverse",
  "censusapi",
  "reshape2",
  "plyr",
  "SciViews",
  "readxl",
  "tidycensus",
  "psych",
  "tigris",
  "spdep",
  "statar",
  "dbplyr"
)

missing_pkgs <- needed_pkgs[
  !vapply(needed_pkgs, requireNamespace, logical(1), quietly = TRUE)
]

if (length(missing_pkgs) > 0) {
  msg <- paste0(
    "The following R packages are missing: ",
    paste(missing_pkgs, collapse = ", "), ".\n\n",
    "Please run renv::restore() in the project root for this year\n",
    "before knitting this document.\n\n",
    "If renv::restore() fails, see the README for this year\n",
    "for operating system–specific setup instructions."
  )
  stop(msg, call. = FALSE)
}

## Global options
options(tigris_use_cache = TRUE)
```

# Introduction

------------------------------------------------------------------------

<br>

The Area Deprivation Index (ADI) is a composite measure of neighborhood-level socioeconomic disadvantage. It was originally developed by Singh (2003) using 1990 U.S. Census data to summarize multiple dimensions of deprivation—such as income, education, employment, housing quality, and household crowding—into a single index. The ADI is calculated for small geographic areas (e.g., census tracts or block groups) and is intended to capture the broader social and economic context in which individuals live.

Methodologically, the ADI is based on factor analysis of 17 census-derived indicators. These indicators are standardized, combined using factor score coefficients (weights) derived from a one-factor solution, and then transformed into a standardized index (traditionally with mean 100 and standard deviation 20). Higher ADI values represent higher levels of area deprivation. Because it is built from public Census/ACS data and uses transparent, interpretable components, the ADI is designed to be scalable across geographies and time.

Kind and colleagues subsequently operationalized and extended the ADI using 2000 Census and later ACS 5-year estimates, and made block-group–level ADI scores publicly available through the Neighborhood Atlas. These products provide national percentile ranks (0–100) and state-specific deciles (0–10), and are often aggregated to tract or county level via population-weighted averages of the underlying block-group scores. As a result, the ADI has been widely adopted in health services research and policy applications, including risk adjustment, resource allocation, and evaluation of health equity initiatives.

The Reproducible Area Deprivation Index (ReADI) builds on this lineage. It retains the core concept of a census-based deprivation index while addressing key methodological limitations in existing implementations and making every step of the construction process fully documented, transparent, and reproducible.

## Reconstructing the Neighborhood Atlas ADI components for Comparison

------------------------------------------------------------------------

<br>

The [Neighborhood Atlas ADI (NA-ADI)](https://www.neighborhoodatlas.medicine.wisc.edu/) is distributed only as final index scores. For all analyses in the manuscript that involve the ADI score itself (e.g., comparisons of ReADI versus NA-ADI scores, model performance using NA-ADI, or policy-relevant contrasts), we use the official NA-ADI scores obtained directly from the Neighborhood Atlas.

However, the underlying code, composite-variable constructions, and intermediate ACS-derived measures used to generate those scores are not publicly available. As a result, it is not possible to perform a direct, code-based replication of the NA-ADI pipeline or to fully audit each transformation step from raw Census/ACS inputs to the final index.

To enable more detailed methodological comparisons (e.g., at the level of individual components or intermediate measures), we reconstructed the NA-ADI components as closely as possible using only the information that is publicly available. Specifically, we: - Used the variable definitions, thresholds, and ACS table references provided in [Kind et al. (2014)](https://www.acpjournals.org/doi/10.7326/M13-2946) and the [Neighborhood Atlas](https://www.neighborhoodatlas.medicine.wisc.edu/) documentation. - Implemented composite measures and transformations (e.g., income disparity, education thresholds, suppression rules) as described in the published materials. - Applied the published factor score coefficients, scaling procedures and the methodological descriptions in [Kind et al. (2014)](https://www.acpjournals.org/doi/10.7326/M13-2946).

We undertook this reconstruction primarily to allow component-level and process-level comparisons with ReADI. For completeness, we also generated corresponding reconstructed NA-ADI scores, but these are used only for internal validation; whenever we report or compare “NA-ADI” scores in the manuscript, those values come directly from the Neighborhood Atlas, not from our reconstruction.

Because we do not have access to the original Neighborhood Atlas source code or to unpublished intermediate files, we cannot guarantee that our reconstructed component-level implementation is identical to the internal NA-ADI pipeline. There may be undocumented decisions (e.g., data cleaning rules, handling of edge cases, or software defaults) that we cannot fully reproduce.

To evaluate how close such reconstructions can be to the official NA-ADI, we collaborated with [Stephen Petterson](https://pmc.ncbi.nlm.nih.gov/articles/PMC10986280/), who independently reverse-engineered the NA-ADI and demonstrated correlations \>0.9999 between his reconstructed scores and the official Neighborhood Atlas values. Our implementation is aligned with this prior work, and comparisons of overlapping versions show similarly high agreement. On this basis, we view our reconstructed NA-ADI components as a best-available, high-fidelity approximation of the underlying Neighborhood Atlas methodology, while explicitly acknowledging that full, line-by-line replication is not possible without direct access to the original code and internal documentation.

# Reverse Enginered NA-ADI Components Preparation

------------------------------------------------------------------------

> Libraries

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code294">Show Code</button>
::: {#code294 .collapse}
```{r, results = F, message = F}
library(tidyverse)
library(censusapi)
library(reshape2) 
library(plyr) 
library(SciViews) 
library(readxl) 
library(tidycensus) 
library(psych)
options(tigris_use_cache = TRUE)
library(tigris)
library(spdep)
library(statar)
```

```{r}
sessionInfo()
```
:::
::::

<br><br>

## Retrieving 2018-2022 5-Year ACS

------------------------------------------------------------------------

<br>

> Pulling Variables Required

<br>

In this section, we obtain the ACS 2018–2022 5-year estimates for the variables needed to reconstruct the Neighborhood Atlas Area Deprivation Index (NA-ADI) component measures and supporting denominators. We compile these inputs at three geographic levels—counties, census tracts, and census block groups—to facilitate comparisons of NA-ADI component structure and related metrics across scales. Definitions of these geographic units are provided in the [U.S. Census Bureau documentation](https://www2.census.gov/geo/pdfs/reference/GARM/Ch10GARM.pdf).

Accessing ACS data via the Census API requires an API key, which can be requested from the [Census Bureau](https://api.census.gov/data/key_signup.html). Once you receive your key, install it in your R environment as the CENSUS_API_KEY environment variable (for example, by adding it to ~/.Renviron or a project .Renviron) and do not hard-code the key directly in shared code.

The code that follows pulls the required ACS variables for counties, census tracts, and census block groups using the Census API and saves them as R objects for use in later steps, where we (i) construct the NA-ADI composite/component variables from raw ACS inputs and (ii) evaluate how these components relate to other measures used in the manuscript.

Below are the final numbers of areas at each geography:

::::: row
::: col-md-4
| Area   | Amount  |
|:-------|:--------|
| CBG    | 242,336 |
| CT     | 85,396  |
| County | 3,222   |
:::
::: col-md-8
:::
:::::

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code357">Show Code</button>
::: {#code357 .collapse}
```{r}
if (identical(Sys.getenv("CENSUS_API_KEY") != "", F)) {
  stop(
    "Census API key not found.\n",
    "Please set the CENSUS_API_KEY environment variable before running this document.\n"
  )
}
states <- setdiff(unique(fips_codes$state_code), c("60", "66", "69", "74", "78")) # Removing US territories

ADI_Vars <- c(
       "B01003_001",
       "B19013_001",
       "B19001_002", "B19001_011", "B19001_012", "B19001_013", "B19001_014", "B19001_015", "B19001_016", "B19001_017", 
       "B17017_002", "B17017_001", 
       "C17002_005", "C17002_004", "C17002_003", "C17002_002", "C17002_001", 
       "B15003_001", "B15003_002", "B15003_003", "B15003_004", "B15003_005", "B15003_006", "B15003_007", "B15003_008", "B15003_009", "B15003_010", "B15003_011", "B15003_012", "B15003_017", "B15003_018", "B15003_019", "B15003_020", "B15003_021", "B15003_022", "B15003_023", "B15003_024", "B15003_025",
       "C24010_003", "C24010_027", "C24010_039", "C24010_063", "C24010_001",
       "B23025_005", "B23025_003",
       "B25077_001", 
       "B25064_001", 
       "B25088_002", 
       "B25008_001", "B25008_002",
       "B25003_001", "B25003_002",
       "B11012_010", "B11012_015", "B11012_001", 
       "B25044_003", "B25044_010", "B25044_001", 
       "B28002_013", "B28002_001",
       "B25016_007", "B25016_016", "B25016_001",
       "B25049_001", "B25049_004", "B25049_007",
       "B25014_005", "B25014_006", "B25014_007", "B25014_011", "B25014_012", "B25014_013", "B25014_001")
  
# CBG level
ACS_CBG <- do.call(rbind, lapply(states, function(st) {
get_acs(
    year = 2022,
    geography = "block group",
    state = st,
    key = Sys.getenv("CENSUS_API_KEY"),
    variables = ADI_Vars)
}))
ACS_CBG <- dcast(ACS_CBG, GEOID + NAME ~ variable, value.var=c("estimate"))
RENA_ADI_2022_CBG_Raw <- ACS_CBG %>% separate(NAME, c("Block_Group", "Tract", "County", "State"), sep = ";")

# CT level
ACS_CT <- do.call(rbind, lapply(states, function(st) {
get_acs(
    year = 2022,
    geography = "tract",
    state = st,
    key = Sys.getenv("CENSUS_API_KEY"),
    variables = ADI_Vars)
}))
ACS_CT <- dcast(ACS_CT, GEOID + NAME ~ variable, value.var=c("estimate"))
RENA_ADI_2022_CT_Raw <- ACS_CT %>% separate(NAME, c("Tract", "County", "State"), sep = ";")

# C level
ACS_C <- do.call(rbind, lapply(states, function(st) {
get_acs(
    year = 2022,
    geography = "county",
    state = st,
    key = Sys.getenv("CENSUS_API_KEY"),
    variables = ADI_Vars)
}))
ACS_C <- dcast(ACS_C, GEOID + NAME ~ variable, value.var=c("estimate"))
RENA_ADI_2022_C_Raw <- ACS_C %>% separate(NAME, c("County", "State"), sep = ",")
```
:::
::::

<br><br>

> Pulling Geography Measures

<br>

In addition to the ACS variables, we retrieve the corresponding spatial geometries for each geography (counties, census tracts, and census block groups). These geometry objects are required for both the spatial imputation procedures and for any visualizations that involve mapping ReADI values. The code in this section downloads and stores the geometry data that will be linked to the ACS variables in later steps.

The area geometry objects used here (ACS_CBG_2022_Geometry, ACS_CT_2022_Geometry, and ACS_C_2022_Geometry) are created in the ReADI construction script [ReADI_2022_Creation.Rmd](https://github.com/ngladish/ReADI/blob/main/2018-2022/ReADI_2022_Creation.Rmd).

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code313">Imputation Function</button>
::: {#code313 .collapse}
```{r}
load(url("https://raw.githubusercontent.com/ngladish/Publications/main/Gladish_2025_ReADI_Creation/Data/ACS_CBG_2022_Geometry.RData"))
load(url("https://raw.githubusercontent.com/ngladish/Publications/main/Gladish_2025_ReADI_Creation/Data/ACS_CT_2022_Geometry.RData"))
load(url("https://raw.githubusercontent.com/ngladish/Publications/main/Gladish_2025_ReADI_Creation/Data/ACS_C_2022_Geometry.RData"))
```
:::
::::

<br><br>

# Imputation

------------------------------------------------------------------------

<br>

We use spatial imputation to address missing values in a small subset of variables prior to constructing the NA-ADI component/composite measures. Neither Kind et al. (2014) nor the Neighborhood Atlas documentation describe whether (or how) missing ACS inputs were handled; therefore, we cannot reproduce any imputation procedure that may have been used in the published NA-ADI scores. At the same time, performing complete-case construction (i.e., dropping any geography with any missing input) would result in a substantial loss of areas. To strike a balance between transparency and coverage, we apply a simplified, reproducible spatial imputation approach similar to the one used in the ReADI pipeline.

For each geography (block group, tract, county), missing values are imputed using neighboring units defined by queen contiguity within state (polygons that share a border or a vertex). In brief, the procedure:

Joins the variable of interest to its corresponding geometry within each state.

Builds a queen-contiguity neighbor list using spdep::poly2nb().

Performs a single imputation pass in which missing values are replaced with the median of their neighbors’ observed values.

Any units that remain missing after this initial pass—typically because they have no neighbors under queen contiguity or because all adjacent neighbors are also missing for that variable—are removed rather than being imputed using higher-level geographic fallback rules.

Units that remain missing after this process are generally geographically isolated (e.g., islands) or correspond to atypical/special-use areas (e.g., national parks or federal facilities), where borrowing information is either not possible or difficult to justify. When running the spatial imputation function you may see warnings such as “some observations have no neighbours” or “neighbour object has X sub-graphs.” These messages are expected for real-world geographies and do not indicate failure: “no neighbours” indicates a polygon cannot borrow information under queen contiguity, and “sub-graphs” indicates disconnected adjacency clusters (e.g., mainland vs islands), with imputation occurring within each cluster.

We do not force additional neighbors (e.g., via large snapping tolerances or k-nearest-neighbor rules) because doing so would introduce arbitrary spatial relationships. This approach provides a transparent compromise: it avoids discarding large numbers of areas due to missingness while also avoiding more complex fallback imputation steps that are not part of the NA-ADI documentation.

> Imputation Functions

The following code defines the reusable functions used for spatial imputation at each geography:

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code723">Imputation Function</button>
::: {#code723 .collapse}
```{r}
impute.fun <- function(data, var, shape) {
  # pull GEOID + variable, rename to "estimate"
  variable <- data[, c("GEOID", var)]
  colnames(variable) <- c("GEOID", "estimate")
  message(paste0(sum(is.na(variable$estimate)), " missing before imputation."))

  # join onto shape and drop invalid geometries
  df <- dplyr::left_join(shape, variable, by = "GEOID")
  df <- df[!is.na(sf::st_dimension(df)), ]

  df$State <- substr(df$GEOID, 1, 2)
  df$raw.estimate <- df$estimate

  n <- nrow(df)
  states <- df$State
  state_levels <- unique(states)

  # precompute row indices per state
  idx_list <- split(seq_len(n), states)

  # precompute neighbour lists per state (geometry only)
  nb_list <- vector("list", length(state_levels))
  names(nb_list) <- state_levels
  for (st in state_levels) {
    idx <- idx_list[[st]]
    nb_list[[st]] <- spdep::poly2nb(df[idx, ], queen = TRUE)
  }

  imputed_last <- rep(NA_real_, n)  # will hold the last round of neighbour medians

  repeat {
    missing_pre <- sum(is.na(df$estimate))

    # compute neighbour medians for current estimates
    imputed <- rep(NA_real_, n)
    for (st in state_levels) {
      idx <- idx_list[[st]]
      est_state <- df$estimate[idx]
      nb_state  <- nb_list[[st]]

      imputed[idx] <- vapply(
        nb_state,
        function(z) stats::median(est_state[z], na.rm = TRUE),
        numeric(1)
      )
    }

    # keep a copy of the latest neighbour medians
    imputed_last <- imputed

    # same logic as before: only fill where estimate is NA
    na_pos <- which(is.na(df$estimate))
    df$estimate[na_pos] <- imputed[na_pos]

    missing_post <- sum(is.na(df$estimate))
    if (missing_post >= missing_pre) break
  }

  # attach the final neighbour-median predictions
  df$imputed <- imputed_last

  message(paste0(sum(is.na(df$estimate)), " missing after imputing."))
  df
}

impute_vars <- function(data, shape, vars, level_label = "") {
  # inner helper for a single variable
  impute_one <- function(var_name) {
    msg_suffix <- if (nzchar(level_label)) paste0(" at ", level_label, " level") else ""
    message("Imputing ", var_name, msg_suffix, " ...")

    df_imp <- impute.fun(
      data  = data,
      var   = var_name,
      shape = shape
    )

    # diagnostics (same as you had)
    message("Correlation (estimate vs raw) for ", var_name)
    print(cor.test(df_imp$estimate, df_imp$raw.estimate))

    message("Correlation (imputed vs raw) for ", var_name)
    print(cor.test(df_imp$imputed, df_imp$raw.estimate))

    # drop geometry, keep GEOID + estimate, rename back to original var name
    df_imp$geometry <- NULL
    out <- df_imp[, c("GEOID", "estimate")]
    names(out)[names(out) == "estimate"] <- var_name

    out
  }

  # run for all vars
  res_list <- lapply(vars, impute_one)

  # combine like your chained plyr::join calls
  imputed <- plyr::join_all(res_list, by = "GEOID", type = "left")

  # NA check (same info you were printing manually)
  na_counts <- sapply(vars, function(v) sum(is.na(imputed[[v]])))
  message("Remaining NAs by variable:")
  print(na_counts)

  imputed
}
```
:::
::::

> Block group (CBG) imputation

At the census block group (CBG) level, spatial imputation is applied to the subset of variables that contain missing values. Only originally missing entries are replaced; observed values are retained unchanged in the final dataset. However, because the imputation model generates predicted (i.e., “imputed”) values for all CBGs during fitting, we can evaluate performance by comparing the model’s predicted values against the observed (non-missing) values. The table below summarizes, for each imputed variable, (1) the correlation between predicted (imputed) and observed values across all CBGs with observed data, (2) the significance of that correlation, and (3) the number of missing values remaining after imputation.

::::: row
::: col-md-6
| Variable   | $r$   | *p*value        | NAs Originally | NAs Remaining |
|:-----------|:------|:----------------|:---------------|:--------------|
| B19013_001 | 0.757 | $<2.2x10^{-16}$ | 14,601 (6)     | 17            |
| B25064_001 | 0.831 | $<2.2x10^{-16}$ | 65,427 (27)    | 29            |
| B25077_001 | 0.918 | $<2.2x10^{-16}$ | 20,796 (9)     | 17            |
| B25088_002 | 0.869 | $<2.2x10^{-16}$ | 29,408 (12)    | 17            |
:::

::: col-md-6
:::
:::::

The code below runs the imputation for block groups and produces the post-imputation dataset used in subsequent ReADI construction steps.

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code581">Show Code</button>
::: {#code581 .collapse}
```{r}
vars <- c("B19013_001", "B25064_001", "B25077_001", "B25088_002")
CBG_2022_Imputed <- impute_vars(
  data        = RENA_ADI_2022_CBG_Raw,
  shape       = ACS_CBG_2022_Geometry,
  vars        = vars,
  level_label = "CBG")
RENA_ADI_CBG_2022_Imp <- RENA_ADI_2022_CBG_Raw[, !names(RENA_ADI_2022_CBG_Raw) %in% vars]
RENA_ADI_CBG_2022_Imp <- plyr::join(RENA_ADI_CBG_2022_Imp, CBG_2022_Imputed, by = "GEOID")
RENA_ADI_CBG_2022_Imp <- RENA_ADI_CBG_2022_Imp[complete.cases(RENA_ADI_CBG_2022_Imp),]
```
:::
::::

> Census Tract (CT)

The same spatial imputation strategy is applied at the census tract and county levels, using tract and county geometries and state-specific neighbor lists. For each geography, only originally missing values are imputed, and imputation proceeds iteratively within state until no additional units can be filled based on their neighbors.

::::: row
::: col-md-6
| Variable   | $r$   | *p*value        | NAs Remaining |
|:-----------|:------|:----------------|:--------------|
| B19013_001 | 0.802 | $<2.2x10^{-16}$ | 4             |
| B25064_001 | 0.839 | $<2.2x10^{-16}$ | 4             |
| B25077_001 | 0.920 | $<2.2x10^{-16}$ | 4             |
| B25088_002 | 0.894 | $<2.2x10^{-16}$ | 4             |
:::

::: col-md-6
:::
:::::

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code639">Show Code</button>
::: {#code639 .collapse}
```{r}
CT_2022_Imputed <- impute_vars(
  data        = RENA_ADI_2022_CT_Raw,
  shape       = ACS_CT_2022_Geometry,
  vars        = vars,
  level_label = "CT")
RENA_ADI_CT_2022_Imp <- RENA_ADI_2022_CT_Raw[, !names(RENA_ADI_2022_CT_Raw) %in% vars]
RENA_ADI_CT_2022_Imp <- plyr::join(RENA_ADI_CT_2022_Imp, CT_2022_Imputed, by = "GEOID")
RENA_ADI_CT_2022_Imp <- RENA_ADI_CT_2022_Imp[complete.cases(RENA_ADI_CT_2022_Imp),]
```
:::
::::

<br><br>

> Counties

The same spatial imputation strategy is applied at the census tract and county levels, using tract and county geometries and state-specific neighbor lists. For each geography, only originally missing values are imputed, and imputation proceeds iteratively within state until no additional units can be filled based on their neighbors.

::::: row
::: col-md-6
| Variable   | $r$   | *p*value        | NAs Remaining |
|:-----------|:------|:----------------|:--------------|
| B19013_001 | 0.782 | $<2.2x10^{-16}$ | 0             |
| B25064_001 | 0.832 | $<2.2x10^{-16}$ | 0             |
| B25077_001 | 0.862 | $<2.2x10^{-16}$ | 0             |
| B25088_002 | 0.858 | $<2.2x10^{-16}$ | 0             |
:::

::: col-md-6
:::
:::::

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code701">Show Code</button>
::: {#code701 .collapse}
```{r}
## Remove DC for spatial imputation
data_no_dc  <- RENA_ADI_2022_C_Raw[RENA_ADI_2022_C_Raw$State != " District of Columbia", ]
geoid_dc    <- RENA_ADI_2022_C_Raw[RENA_ADI_2022_C_Raw$State == " District of Columbia", "GEOID"]
shape_no_dc <- ACS_C_2022_Geometry[!ACS_C_2022_Geometry$GEOID %in% geoid_dc, ]

C_2022_Imputed <- impute_vars(
  data        = data_no_dc,
  shape       = shape_no_dc,
  vars        = vars,
  level_label = "county (excluding DC)")

RENA_ADI_C_2022_Imp <- RENA_ADI_2022_C_Raw[, !names(RENA_ADI_2022_C_Raw) %in% vars]
RENA_ADI_C_2022_Imp <- plyr::join(RENA_ADI_C_2022_Imp, C_2022_Imputed, by = "GEOID")

stopifnot(identical(RENA_ADI_2022_C_Raw$GEOID, RENA_ADI_C_2022_Imp$GEOID))

## Restore DC’s original values (they were excluded from imputation)
for (v in vars) {
  RENA_ADI_C_2022_Imp[[v]] <- ifelse(
    is.na(RENA_ADI_C_2022_Imp[[v]]),
    RENA_ADI_2022_C_Raw[[v]],
    RENA_ADI_C_2022_Imp[[v]]
  )}
```
:::
::::

<br><br>

# Reverse Engineering of NA-ADI Components

------------------------------------------------------------------------

<br>

## Method

<br>

Using the already-acquired and imputed ACS inputs for each geography, we reconstruct the NA-ADI component/composite measures by applying the published formulas and thresholds to the relevant ACS table cells, as described by Kind et al. (2014), [Singh (2003)](https://ajph.aphapublications.org/doi/pdf/10.2105/AJPH.93.7.1137), and the [Neighborhood Atlas](https://www.neighborhoodatlas.medicine.wisc.edu/) documentation (Table below). For each geographic unit, we compute the derived indicators (e.g., proportions, medians, and log-ratios) directly from ACS numerators and denominators. After construction, any missing values that arise solely from structural zeros (i.e., 0/0 cases where both the numerator and denominator are zero) are set to zero to prevent undefined values from propagating. The resulting component dataset is then restricted to GEOID and the constructed measures and saved as an R object for downstream merging with the published NA-ADI ranks and for component-level analyses.

:::: {style="margin:16px 0"}
<center><button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code1111"><h4 class="text-white">CBG NA-ADI Variables</h4></button></center>
::: {#code1111 .collapse}
| Census Variable | Name | Table | <center>Formula</center> |
|-----------------------------|------------|------------|:-----------------:|
| Median family income, \$ | MEDFI | B19013 | $001$ |
| Income disparity$^a$ | INCDIS | B19001 | $-ln({002+1\over\sum(011-017)+1}x100)$\| |
| Families below poverty level, % | BELPL | B17017 | ${002\over001}x100$ |
| Population below 150% of the poverty threshold, % | PL150 | C17002 | ${\sum(002-005)\over 001}x100$ |
| Population ≥25y with \<9y school, % | EDU9YR | B15003 | ${\sum(002-012)\over 001}x100$ |
| Population ≥25y with at least a highschool diploma, % | HSDPNHIGH | B15003 | ${\sum(017-025)\over 001}x100$ |
| Employed persons ≥16y in white-collar occupations, % | EMPWC | C24010 | ${\sum(003,027,039,063)\over 001}x100$ |
| Civilian labor force population ≥16 y unemployed, % | UNEMP | B23025 | ${005\over003}x100$ |
| Median home value, \$ | MEDHV | B25077 | $001$ |
| Median gross rent, \$ | MEDRNT | B25064 | $001$ |
| Median monthly mortgage, \$ | MEDMORT | B25088 | $002$ |
| Owner-occupied housing units, % | OWN | B25008 | ${002\over001}x100$ |
| Single-parent households with children \<18y, % | SNGPNT | B11012 | ${\sum(010,015)\over 001}x100$ |
| Households without a motor vehicle, % | NOVEH | B25044 | ${\sum(010,003)\over 001}x100$ |
| Households without internet, % | NOINT | B28002 | ${013\over001}x100$ |
| Occupied housing units without complete plumbing, % | NOPLUM | B25016 | $-ln({\sum(007,016)+1\over001+1}x100)$ |
| Households with more than 1 person per room, % | CROWD | B25014 | ${\sum(005-007,011-013)\over 001}x100$ |

<sup>$^a$ Income disparity in Singh was defined as the log of 100×ratio of number of households with \<\$10,000 income to number of households with ≥\$50,000 income.</sup>
:::
::::

<br><br>

### Block group (CBG) NA-ADI

<br>

The table describes the amount of NAs which resulted from the 17 variable calculations and which were subsequently converted to 0 and the weights resulting from factor analysis. The code produced several products, the zscore standardized 17 composite variables, a raw ReADI score which can be used to subset down to whichever geographical area is relevant for a user's purposed and then re-scaled from 0-100, and then a nationally representative ADI scaled from 0-100. The ReADI_2022_CBG_RawVars.RData file has the 17 variables prior to zscore them.

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code1019">Show Code</button>
::: {#code1019 .collapse}
```{r}
RENA_ADI_CBG_2022 <- dplyr::mutate(RENA_ADI_CBG_2022_Imp,
    MEDFI = B19013_001,
    INCDIS = log(100*((B19001_002 + 1)/(B19001_011 + B19001_012 + B19001_013 + B19001_014 + B19001_015 + B19001_016 + B19001_017 + 1))),
    BELPL = B17017_002/B17017_001*100,
    PL150 = (C17002_005 + C17002_004 + C17002_003 + C17002_002)/C17002_001*100,
    EDU9YR = (B15003_002 + B15003_003 + B15003_004 + B15003_005 + B15003_006 + B15003_007 + B15003_008 + B15003_009 + B15003_010 + B15003_011 + B15003_012)/B15003_001*100,
    HSDPNHIGH = (B15003_017 + B15003_018 + B15003_019 + B15003_020 + B15003_021 + B15003_022 + B15003_023 + B15003_024 + B15003_025)/B15003_001*100,
    EMPWC = (C24010_003 + C24010_027 + C24010_039 + C24010_063)/C24010_001*100,
    UNEMP = B23025_005/B23025_003*100,
    MEDHV = B25077_001,
    MEDRNT = B25064_001,
    MEDMORT = B25088_002,
    OWN = B25008_002/B25008_001*100,
    SNGPNT = (B11012_010 + B11012_015)/B11012_001*100,
    NOVEH = (B25044_010 + B25044_003)/B25044_001*100,
    NOINT = B28002_013/B28002_001*100,
    NOPLUM = log((B25016_007 + B25016_016 + 1)/(B25016_001 + 1)*100),
    CROWD = (B25014_005 + B25014_006 + B25014_007 + B25014_011 + B25014_012 + B25014_013)/B25014_001*100,
) %>%
  select(GEOID, Block_Group, Tract, County, State, MEDFI, INCDIS, BELPL, PL150, EDU9YR, HSDPNHIGH, EMPWC, UNEMP, MEDHV, MEDRNT, MEDMORT, OWN, SNGPNT, NOVEH, NOINT, NOPLUM, CROWD)

# Replacing NA values resulting from 0 values back to 0. 
colSums(is.na(RENA_ADI_CBG_2022_Imp))
colSums(is.na(RENA_ADI_CBG_2022))
RENA_ADI_CBG_2022[is.na(RENA_ADI_CBG_2022)] <- 0
RENA_ADI_2022_CBG_RawVars <- RENA_ADI_CBG_2022
save(RENA_ADI_2022_CBG_RawVars, file = "RENA_ADI_2022_CBG_RawVars.RData")
```
:::
::::

<br><br>

### Census tract (CT) NA-ADI

<br>

The table describes the amount of NAs which resulted from the 17 variable calculations and which were subsequently converted to 0 and the weights resulting from factor analysis. The code produced several products, the zscore standardized 17 composite variables, a raw ReADI score which can be used to subset down to whichever geographical area is relevant for a user's purposed and then re-scaled from 0-100, and then a nationally representative ADI scaled from 0-100. The ReADI_2022_CBG_RawVars.RData file has the 17 variables prior to zscore them.

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code1019">Show Code</button>
::: collapse
```{r}
RENA_ADI_CT_2022 <- dplyr::mutate(RENA_ADI_CT_2022_Imp,
    MEDFI = B19013_001,
    INCDIS = log(100*((B19001_002 + 1)/(B19001_011 + B19001_012 + B19001_013 + B19001_014 + B19001_015 + B19001_016 + B19001_017 + 1))),
    BELPL = B17017_002/B17017_001*100,
    PL150 = (C17002_005 + C17002_004 + C17002_003 + C17002_002)/C17002_001*100,
    EDU9YR = (B15003_002 + B15003_003 + B15003_004 + B15003_005 + B15003_006 + B15003_007 + B15003_008 + B15003_009 + B15003_010 + B15003_011 + B15003_012)/B15003_001*100,
    HSDPNHIGH = (B15003_017 + B15003_018 + B15003_019 + B15003_020 + B15003_021 + B15003_022 + B15003_023 + B15003_024 + B15003_025)/B15003_001*100,
    EMPWC = (C24010_003 + C24010_027 + C24010_039 + C24010_063)/C24010_001*100,
    UNEMP = B23025_005/B23025_003*100,
    MEDHV = B25077_001,
    MEDRNT = B25064_001,
    MEDMORT = B25088_002,
    OWN = B25008_002/B25008_001*100,
    SNGPNT = (B11012_010 + B11012_015)/B11012_001*100,
    NOVEH = (B25044_010 + B25044_003)/B25044_001*100,
    NOINT = B28002_013/B28002_001*100,
    NOPLUM = log((B25016_007 + B25016_016 + 1)/(B25016_001 + 1)*100),
    CROWD = (B25014_005 + B25014_006 + B25014_007 + B25014_011 + B25014_012 + B25014_013)/B25014_001*100,
) %>%
  select(GEOID, Tract, County, State, MEDFI, INCDIS, BELPL, PL150, EDU9YR, HSDPNHIGH, EMPWC, UNEMP, MEDHV, MEDRNT, MEDMORT, OWN, SNGPNT, NOVEH, NOINT, NOPLUM, CROWD)

# Replacing NA values resulting from 0 values back to 0. 
colSums(is.na(RENA_ADI_CT_2022))
RENA_ADI_CT_2022[is.na(RENA_ADI_CT_2022)] <- 0
RENA_ADI_2022_CT_RawVars <- RENA_ADI_CT_2022
save(RENA_ADI_2022_CT_RawVars, file = "RENA_ADI_2022_CT_RawVars.RData")
```
:::
::::

<br><br>

### County (C) NA-ADI

<br>


The table describes the amount of NAs which resulted from the 17 variable calculations and which were subsequently converted to 0 and the weights resulting from factor analysis. The code produced several products, the zscore standardized 17 composite variables, a raw ReADI score which can be used to subset down to whichever geographical area is relevant for a user's purposed and then re-scaled from 0-100, and then a nationally representative ADI scaled from 0-100. The ReADI_2022_CBG_RawVars.RData file has the 17 variables prior to zscore them.

:::: {style="margin:16px 0"}
<button type="button" class="btn btn-dark" control-id="ControlID-54" data-bs-toggle="collapse" data-bs-target="#code1019">Show Code</button>
::: collapse
```{r}
RENA_ADI_C_2022 <- dplyr::mutate(RENA_ADI_C_2022_Imp,
    MEDFI = B19013_001,
    INCDIS = log(100*((B19001_002 + 1)/(B19001_011 + B19001_012 + B19001_013 + B19001_014 + B19001_015 + B19001_016 + B19001_017 + 1))),
    BELPL = B17017_002/B17017_001*100,
    PL150 = (C17002_005 + C17002_004 + C17002_003 + C17002_002)/C17002_001*100,
    EDU9YR = (B15003_002 + B15003_003 + B15003_004 + B15003_005 + B15003_006 + B15003_007 + B15003_008 + B15003_009 + B15003_010 + B15003_011 + B15003_012)/B15003_001*100,
    HSDPNHIGH = (B15003_017 + B15003_018 + B15003_019 + B15003_020 + B15003_021 + B15003_022 + B15003_023 + B15003_024 + B15003_025)/B15003_001*100,
    EMPWC = (C24010_003 + C24010_027 + C24010_039 + C24010_063)/C24010_001*100,
    UNEMP = B23025_005/B23025_003*100,
    MEDHV = B25077_001,
    MEDRNT = B25064_001,
    MEDMORT = B25088_002,
    OWN = B25008_002/B25008_001*100,
    SNGPNT = (B11012_010 + B11012_015)/B11012_001*100,
    NOVEH = (B25044_010 + B25044_003)/B25044_001*100,
    NOINT = B28002_013/B28002_001*100,
    NOPLUM = log((B25016_007 + B25016_016 + 1)/(B25016_001 + 1)*100),
    CROWD = (B25014_005 + B25014_006 + B25014_007 + B25014_011 + B25014_012 + B25014_013)/B25014_001*100,
) %>%
  select(GEOID, County, State, MEDFI, INCDIS, BELPL, PL150, EDU9YR, HSDPNHIGH, EMPWC, UNEMP, MEDHV, MEDRNT, MEDMORT, OWN, SNGPNT, NOVEH, NOINT, NOPLUM, CROWD)

# Replacing NA values resulting from 0 values back to 0. 
colSums(is.na(RENA_ADI_C_2022))
RENA_ADI_C_2022[is.na(RENA_ADI_C_2022)] <- 0
RENA_ADI_2022_C_RawVars <- RENA_ADI_C_2022
save(RENA_ADI_2022_C_RawVars, file = "RENA_ADI_2022_C_RawVars.RData")
```
:::
::::

<br><br>
